---
title: "Fitting model 39"
output: 
  html_document:
    toc: TRUE
---


Load all important libraries
```{r setup, message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.height = 10)
knitr::opts_chunk$set(fig.width = 15)
library(dMod)
library(stringr) # Um bequem mit strings zu arbeiten
library(tidyverse) # Viele Funktionen, u.a. für data.frames und ggplot2 für schöne plots
library(magrittr) # der Pipe-operator %>%: z.B: x =" a; y="f(x); z="g(y); wird zu z=" a %>% f %>% g
library(conveniencefunctions)



# load("2018_03_09_17_17_workspace.rda")
# for(i in lsdMod(classlist = "prdfn")) {loadDLL(i)}
```


# Read model
```{r}
source("../model/limax_pkpd_v41.R")
```


```{r}
pars_raw <- c(x0, p) 
pars_in_dxdtdmod <- c(getSymbols(dxdt_dmod), names(dxdt_dmod))
```

# Odemodels and predicition function

## Apap
```{r odemodel_apap}
free_pars_apap <- c("Ka_apap", "APAPD_HLM_CL", "APAPD_Km_apap")
odemodel_apap <- odemodel(dxdt_dmod, modelname = "odemodel_apap", fixed = setdiff(pars_in_dxdtdmod, c(free_pars_apap, "Aar_apap"))) # Aar_apap is not there to be optimized, but a variable which is a state is needed because of a bug in odemodel.

x_apap <- Xs(odemodel_apap)
```


## Bicarbonate

```{r odemodel_bic}
free_pars_bic <- c("Ka_co2c13", "KLU_EXCO2", "CO2FIX_HLM_CL", "KBO_FIXCO2", "KBO_RELCO2", "KBO_MAXCO2")
odemodel_bic <- odemodel(dxdt_dmod, modelname = "odemodel_bic", fixed = setdiff(pars_in_dxdtdmod, c(free_pars_bic, "Aar_apap"))) # Aar_apap is not there to be optimized, but a variable which is a state is needed because of a bug in odemodel.

x_bic <- Xs(odemodel_bic)
```

## Metc13

```{r odemodel_met}
free_pars_met <- c("Ka_metc13", "CYP1A2MET_CL", "CYP1A2MET_Km_met")
odemodel_met <- odemodel(dxdt_dmod, modelname = "odemodel_met", fixed = setdiff(pars_in_dxdtdmod, c(free_pars_met, "Aar_apap"))) # Aar_apap is not there to be optimized, but a variable which is a state is needed because of a bug in odemodel.

x_met <- Xs(odemodel_met)
```

## Combined

```{r odemodel_apap_bic_met}
free_pars_apap_bic_met <- c(free_pars_apap, free_pars_bic, free_pars_met) %>% unique
odemodel_apap_bic_met <- odemodel(dxdt_dmod, modelname = "odemodel_apap_bic_met", fixed = setdiff(pars_in_dxdtdmod, c(free_pars_apap_bic_met, "Aar_apap"))) # Aar_apap is not there to be optimized, but a variable which is a state is needed because of a bug in odemodel.

x_apap_bic_met <- Xs(odemodel_apap_bic_met)
```





# Observation functions

## Apap

```{r g_apap}
observables_apap <- y_dmod[c("Mve_apap")] %>% set_names(c("Mve_apap"))
g_apap <- Y(g = observables_apap, f = x_apap)
```

## Bicarbonate

```{r g_bic}
recovery_bic <- paste(y_dmod["Exhalation_co2c13"], "/ 60 * Mr_co2c13 / Ri_co2c13 * 100")
observables_bic <- c(recovery_bic, y_dmod[c("DOB", "P_CO2Fc13")])
names(observables_bic) <- c("cum_rec_co2c13", "DOB", "P_CO2F")

observables_bic["P_CO2F"] <- paste0(observables_bic["P_CO2F"], " + offset_bic")

g_bic <- Y(observables_bic, x_bic)
```

## Metc13

```{r g_met}
recovery_met <- paste(y_dmod["Exhalation_co2c13"], "/ init_PODOSE_metc13 * Mr_metc13 * 100" )
cum_met <- paste( "Abreath_co2c13/ init_PODOSE_metc13 * Mr_metc13 * 100")
observables_met <- c(recovery_met, cum_met) %>% set_names(c("mom_rec_metc13", "cum_rec_metc13"))

g_met <- Y(observables_met, x_met)
```

## Combined

```{r g_apap_bic_met}
observables_apap_bic_met <- c(observables_apap, observables_bic, observables_met)
g <- Y(observables_apap_bic_met, x_apap_bic_met)
```

# Data 
Read data, insert the default values for the parameters supplied in the data sheet. 

* Taheri rausschmeißen zum Fitten

```{r, message=FALSE}
data <-
  read_tsv("../data/limax_pkpd_v41_data.csv") %>% 
  select(-model, -subjects) %>% 
  rename(name = observer)
supplied_pars <- names(pars_raw)[(names(pars_raw) %in% names(data))]
```


# Parameter trafos
## Apap
```{r p_apap}
apap_factors <- c("study", "group", "name", "BW", "PODOSE_apap", "IVDOSE_apap", 
"PODOSE_co2c13", "IVDOSE_co2c13", "Ri_co2c13", "ti_co2c13", "PODOSE_metc13", 
"IVDOSE_metc13", "ti_metc13")
data_apap <- read_tsv("../data/limax_pkpd_v41_data.csv") %>% 
  select(-model) %>% 
  rename(n = subjects) %>% 
  rename(name = observer) %>% 
  filter(simulation == "apap") %>% 
  select(-simulation) %>% 
  as.data.frame() %>% 
  fitErrorModel(factors = apap_factors) %>% 
  select(-n) %>% 
  as.data.frame()
  
outer_pars_apap <- sort(c(supplied_pars, free_pars_apap))

trafo_apap <-
  pars_raw %>% 
  sort_by_name() %>% 
  replace((names(.) %in% outer_pars_apap), outer_pars_apap) %>% 
  
  branch(data_apap %>% as.datalist() %>% covariates()) %>% 
  
  minsert(supplied_pars) %>% 
  
  insert("x~exp(X)", x = free_pars_apap, X = toupper(free_pars_apap)) # backtrafo to linear pars from log-pars

p_apap <- P(trafo_apap)

pars_apap <- log(pars_raw[free_pars_apap]) %>% set_names(toupper(free_pars_apap))
```

### Test plot
```{r plot_apap, eval=TRUE}
# loadDLL(x_apap)
times <- seq(0,24, 0.1)
plotCombined((g_apap*x_apap*p_apap)(times, pars_apap, deriv = F), data = data_apap %>% as.datalist(), name %in% names(observables_apap))

obj <- normL2(data_apap %>% as.datalist, (g_apap*x_apap*p_apap))
obj(getParameters(obj) %>% are_names_of(0))
```

## Bicarbonate

Some studies don't have sigmas. Estimate the errors for them while fitting. For this, we need to define an error model.
1. Split the data into studies a) with errors "_bic" and b) without errors "_bic_sigma_NA"
2. Define the error model (technically, this will also be an observation function: It "observes" the outputs of the model, e.g. "recovery", and calculates another variable from it, the error)
3. For both sets of data, "_bic", and "bic_sigma_NA", we now need condition specific parameters. Additionally, in "_bic_sigma_NA", we need to supply the parameters of our error model.

### Error model

```{r e_bic}
data_bic <- data %>% 
  filter(simulation == "bicarbonate")%>% 
  select(-simulation) %>% 
  as.data.frame()

studies_with_sigma_na <- data_bic %>% filter(is.na(sigma)) %>% .[["study"]] %>% unique
data_bic_sigma_NA <- data_bic %>% filter(study %in% studies_with_sigma_na)
data_bic <- data_bic %>% filter(! study %in% studies_with_sigma_na)

errors_bic_sigma_NA <- paste0("sqrt(s0_", names(observables_bic), "^2 + srel_", names(observables_bic), "^2 * ", names(observables_bic), "^2 )") %>% set_names(names(observables_bic))

e_bic_sigma_NA <- Y(g = errors_bic_sigma_NA, f= (g_bic))
```

### Parameter trafo
```{r p_bic}
outer_pars_bic <- sort(c(supplied_pars, free_pars_bic))

trafo_bic<-
  c(pars_raw) %>% 
  sort_by_name() %>% 
  replace((names(.) %in% outer_pars_bic), outer_pars_bic) %>% 
  
  branch(data_bic %>% as.datalist() %>% covariates()) %>% # The table of covariates includes dosepar and dose, which are used in the next line
  
  minsert(supplied_pars) %>% 

  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) %>% 
  
  define("x~x", x = "offset_bic")

p_bic <- P(trafo_bic)

pars_bic <- getParameters(p_bic) %>% are_names_of(0)
```

```{r p_bic_sigma_NA}
pars_errors_bic_sigma_NA <- getSymbols(errors_bic_sigma_NA) %>% str_subset("^s") %>% are_names_of(1)

outer_pars_bic <- sort(c(supplied_pars, free_pars_bic, names(pars_errors_bic_sigma_NA)))

trafo_bic_sigma_NA <-
  c(pars_raw, pars_errors_bic_sigma_NA) %>% 
  sort_by_name() %>% 
  replace((names(.) %in% outer_pars_bic), outer_pars_bic) %>% 
  
  branch(data_bic_sigma_NA %>% as.datalist() %>% covariates()) %>% # The table of covariates includes dosepar and dose, which are used in the next line
  
  minsert(supplied_pars) %>% 
  
  insert("s~s_study", s = names(pars_errors_bic_sigma_NA), study = study) %>% 
  
  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) %>% 
  
  insert("x~0", x = c("S0_CO2_RATIO_BIC_BARSTOW1990", "S0_RECOVERY_BIC_BARSTOW1990", 
"SREL_CO2_RATIO_BIC_BARSTOW1990", "SREL_RECOVERY_BIC_BARSTOW1990", 
"S0_DOB_BIC_MEINEKE1993", "S0_RECOVERY_BIC_MEINEKE1993", "SREL_DOB_BIC_MEINEKE1993", 
"SREL_RECOVERY_BIC_MEINEKE1993")) %>% 
  
  define("x~x", x = "offset_bic")

p_bic_sigma_NA <- P(trafo_bic_sigma_NA)

pars_bic_sigma_NA <- getParameters(p_bic_sigma_NA) %>% are_names_of(0)

# p_bic_sigma_NA(pars_bic_sigma_NA)
```

### Example plot
```{r}
loadDLL(x_bic)
(g_bic*x_bic*p_bic_sigma_NA)(times*10, pars_bic_sigma_NA, deriv = F) %>%  plotPrediction(name %in% names(observables_bic))
(g_bic*x_bic*p_bic)(times*10, pars_bic, deriv = F) %>%  
  # lapply(. %>% as.tibble)
  plotPrediction(name %in% names(observables_bic))
# obj <- normL2(data_bic %>% as.datalist,(g_bic*x_bic*p_bic))

```


## Metc13

The same game for the data sets without sigmas applies here. Read the description for Bic.

### Error model
```{r e_met}
data_met <- data %>% 
  filter(simulation == "methacetin")%>% 
  select(-simulation) %>% 
  as.data.frame()

studies_with_sigma_na <- data_met %>% filter(is.na(sigma)) %>% .[["study"]] %>% unique
data_met_sigma_NA <- data_met %>% filter(study %in% studies_with_sigma_na)
data_met <- data_met %>% filter(! study %in% studies_with_sigma_na)

errors_met_sigma_NA <- paste0("sqrt(s0_", names(observables_met), "^2 + srel_", names(observables_met), "^2 * ", names(observables_met), "^2)") %>% set_names(names(observables_met))

e_met_sigma_NA <- Y(g = errors_met_sigma_NA, f= (g_met))
```

### Parameter trafo
```{r p_met}
outer_pars_met <- sort(c(supplied_pars, free_pars_met))

trafo_met<-
  c(pars_raw) %>% 
  sort_by_name() %>% 
  replace((names(.) %in% outer_pars_met), outer_pars_met) %>% 
  
  branch(data_met %>% as.datalist() %>% covariates()) %>%  # The table of covariates includes dosepar and dose, which are used in the next line
  
  minsert(supplied_pars) %>% 

  define("init_PODOSE_metc13~podose", podose = mytrafo[[i]]["PODOSE_metc13"]) %>% # For the observables, I need the initial dose as a fixed parameter which doesn't change. Because the PODOSE_metc13 is also a state, I need to duplicate this parameters
    
  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) 

p_met <- P(trafo_met)

pars_met <- getParameters(p_met) %>% are_names_of(0)
```


```{r p_met_sigma_NA}
pars_errors_met_sigma_NA <- getSymbols(errors_met_sigma_NA) %>% str_subset("^s") %>%  are_names_of(1)

outer_pars_met <- sort(c(supplied_pars, free_pars_met, names(pars_errors_met_sigma_NA)))

trafo_met_sigma_NA <-
  c(pars_raw, pars_errors_met_sigma_NA) %>% 
  sort_by_name() %>% 
  replace((names(.) %in% outer_pars_met), outer_pars_met) %>% 
  
  branch(data_met_sigma_NA %>% as.datalist() %>% covariates()) %>% # The table of covariates includes dosepar and dose, which are used in the next line
  
  minsert(supplied_pars) %>% 
  
  define("init_PODOSE_metc13~podose", podose = mytrafo[[i]]["PODOSE_metc13"]) %>% # For the observables, I need the initial dose as a fixed parameter which doesn't change. Because the PODOSE_metc13 is also a state, I need to duplicate this parameters
  
  insert("s~s_study", s = names(pars_errors_met_sigma_NA), study = study) %>% 
  
  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) %>% 
  insert("x~0", x = c("S0_CUM_MET_KRUMBIEGEL1985", "SREL_CUM_MET_KRUMBIEGEL1985"))
  


p_met_sigma_NA <- P(trafo_met_sigma_NA)

pars_met_sigma_NA <- getParameters(p_met_sigma_NA) %>% are_names_of(0)
```

### Example plot
```{r}
loadDLL(x_met)
(g_met*x_met*p_met_sigma_NA)(times*100, pars_met_sigma_NA, deriv = F) %>% plotPrediction(name %in% names(observables_met))
```



# Bic and met together
```{r x, g and e bicmet}
free_pars_bicmet <- c(free_pars_bic, free_pars_met)
odemodel_bicmet <- odemodel(dxdt_dmod, modelname = "odemodel_bicmet", fixed = setdiff(pars_in_dxdtdmod, c(free_pars_bicmet, "Aar_apap"))) # Aar_apap is not there to be optimized, but a variable which is a state is needed because of a bug in odemodel.
x_bicmet <- Xs(odemodel_bicmet)

g_bicmet <- Y(c(observables_bic, observables_met), x_bicmet)

e_bicmet <- Y(c(errors_bic_sigma_NA, errors_met_sigma_NA), g_bicmet)
```

```{r data and p bicmet}
data_bicmet <- rbind(data_bic, data_met)
data_bicmet_sigma_NA <- rbind(data_bic_sigma_NA, data_met_sigma_NA)

outer_pars_bic <- sort(c(supplied_pars, free_pars_bic))
outer_pars_bic_sigma_NA <- sort(c(supplied_pars, free_pars_bic, names(pars_errors_bic_sigma_NA)))

outer_pars_met <- sort(c(supplied_pars, free_pars_met))
outer_pars_met_sigma_NA <- sort(c(supplied_pars, free_pars_met, names(pars_errors_met_sigma_NA)))

trafo_bicmet<-
  c(pars_raw) %>% 
  sort_by_name() %>% 
  replace((names(.) %in% unique(c(outer_pars_bic, outer_pars_met))), sort(unique(c(outer_pars_bic, outer_pars_met)))) %>% 
  
  branch(data_bicmet %>% as.datalist() %>% covariates()) %>% # The table of covariates includes dosepar and dose, which are used in the next line
  
  minsert(supplied_pars) %>% 

  define("init_PODOSE_metc13~podose", podose = mytrafo[[i]]["PODOSE_metc13"]) %>% # For the observables, I need the initial dose as a fixed parameter which doesn't change. Because the PODOSE_metc13 is also a state, I need to duplicate this parameters

  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) %>% 
  
  define("x~x", x = "offset_bic")


trafo_bicmet_sigma_NA <-
  c(pars_raw, pars_errors_bic_sigma_NA, pars_errors_met_sigma_NA) %>% 
  sort_by_name() %>% 
  replace((names(.) %in% unique(c(outer_pars_bic_sigma_NA, outer_pars_met_sigma_NA))), sort(unique(c(outer_pars_bic_sigma_NA, outer_pars_met_sigma_NA)))) %>% 
  
  branch(data_bicmet_sigma_NA %>% as.datalist() %>% covariates()) %>% # The table of covariates includes dosepar and dose, which are used in the next line
  minsert(supplied_pars) %>% 
  #bic
  insert("s~s_study", s = names(pars_errors_bic_sigma_NA), study = unique(data_bic_sigma_NA$study)) %>% 

  #met
  insert("s~s_study", s = names(pars_errors_met_sigma_NA), study = unique(data_met_sigma_NA$study)) %>% 
  define("init_PODOSE_metc13~podose", podose = mytrafo[[i]]["PODOSE_metc13"]) %>% # For the observables, I need the initial dose as a fixed parameter which doesn't change. Because the PODOSE_metc13 is also a state, I need to duplicate this parameters

  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) %>% 
  
  #bic
  insert("x~0", x = c("S0_CO2_RATIO_BIC_BARSTOW1990", "S0_RECOVERY_BIC_BARSTOW1990", 
"SREL_CO2_RATIO_BIC_BARSTOW1990", "SREL_RECOVERY_BIC_BARSTOW1990", 
"S0_DOB_BIC_MEINEKE1993", "S0_RECOVERY_BIC_MEINEKE1993", "SREL_DOB_BIC_MEINEKE1993", 
"SREL_RECOVERY_BIC_MEINEKE1993")) %>% 
  define("x~x", x = "offset_bic") %>% 
  
  #met
  insert("x~0", x = c("S0_CUM_MET_KRUMBIEGEL1985", "SREL_CUM_MET_KRUMBIEGEL1985"))



p_bicmet <- P(trafo_bicmet)
pars_bicmet <- getParameters(p_bicmet) %>% are_names_of(0)

p_bicmet_sigma_NA <- P(trafo_bicmet_sigma_NA)
pars_bicmet_sigma_NA <- getParameters(p_bicmet_sigma_NA) %>% are_names_of(0)
```

# Apap, bic and met

```{r x, g and e apapbicmet}
free_pars_apapbicmet <- c(free_pars_apap, free_pars_bic, free_pars_met)
odemodel_apapbicmet <- odemodel(dxdt_dmod, modelname = "odemodel_apapbicmet", fixed = setdiff(pars_in_dxdtdmod, c(free_pars_apapbicmet, "Aar_apap"))) # Aar_apap is not there to be optimized, but a variable which is a state is needed because of a bug in odemodel.
x_apapbicmet <- Xs(odemodel_apapbicmet)

g_apapbicmet <- Y(c(observables_apap, observables_bic, observables_met), x_apapbicmet)

e_apapbicmet <- Y(c(errors_bic_sigma_NA, errors_met_sigma_NA), g_apapbicmet)
```

```{r data and p apapbicmet}
data_apapbicmet <- rbind(data_apap, data_bic, data_met)
data_apapbicmet_sigma_NA <- rbind(data_bic_sigma_NA, data_met_sigma_NA)

outer_pars_apap <- sort(c(supplied_pars,free_pars_apap))

outer_pars_bic <- sort(c(supplied_pars, free_pars_bic))
outer_pars_bic_sigma_NA <- sort(c(supplied_pars, free_pars_bic, names(pars_errors_bic_sigma_NA)))

outer_pars_met <- sort(c(supplied_pars, free_pars_met))
outer_pars_met_sigma_NA <- sort(c(supplied_pars, free_pars_met, names(pars_errors_met_sigma_NA)))

outer_pars_apapbicmet <- sort(unique(c(outer_pars_apap, outer_pars_bic, outer_pars_met)))
outer_pars_apapbicmet_sigma_NA <- sort(unique(c(outer_pars_apap, outer_pars_bic, outer_pars_bic_sigma_NA, outer_pars_met,outer_pars_met_sigma_NA)))

trafo_apapbicmet<-
  c(pars_raw) %>% 
  sort_by_name() %>% 
  replace(names(.) %in% outer_pars_apapbicmet, outer_pars_apapbicmet) %>% 
  
  branch(data_apapbicmet %>% as.datalist() %>% covariates()) %>% # The table of covariates includes dosepar and dose, which are used in the next line
  
  minsert(supplied_pars) %>% 
  
  define("init_PODOSE_metc13~podose", podose = mytrafo[[i]]["PODOSE_metc13"]) %>% # For the observables, I need the initial dose as a fixed parameter which doesn't change. Because the PODOSE_metc13 is also a state, I need to duplicate this parameters
  
  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) %>% 
  
  define("x~x", x = "offset_bic")


trafo_apapbicmet_sigma_NA <-
  c(pars_raw, pars_errors_bic_sigma_NA, pars_errors_met_sigma_NA) %>% 
  sort_by_name() %>% 
  replace(names(.) %in% outer_pars_apapbicmet_sigma_NA, outer_pars_apapbicmet_sigma_NA) %>% 
  
  branch(data_apapbicmet_sigma_NA %>% as.datalist() %>% covariates()) %>% # The table of covariates includes dosepar and dose, which are used in the next line
  minsert(supplied_pars) %>% 
  #bic
  # insert("s~s_study", s = names(pars_errors_bic_sigma_NA), study = unique(data_bic_sigma_NA$study)) %>% 
  
  #met
  insert("s~s_study", s = names(pars_errors_met_sigma_NA), study = unique(data_met_sigma_NA$study)) %>% 
  define("init_PODOSE_metc13~podose", podose = mytrafo[[i]]["PODOSE_metc13"]) %>% # For the observables, I need the initial dose as a fixed parameter which doesn't change. Because the PODOSE_metc13 is also a state, I need to duplicate this parameters
  
  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) %>% 
  
  #bic
  # insert("x~0", x = c("S0_CUM_REC_CO2C13_BARSTOW1990", "S0_P_CO2F_BARSTOW1990", 
  #                     "SREL_CO2_RATIO_BIC_BARSTOW1990", "SREL_RECOVERY_BIC_BARSTOW1990", 
  #                     "S0_DOB_BIC_MEINEKE1993", "S0_RECOVERY_BIC_MEINEKE1993", "SREL_DOB_BIC_MEINEKE1993", 
  #                     "SREL_RECOVERY_BIC_MEINEKE1993")) %>% 
  define("x~x", x = "offset_bic") %>% 
  
  #met
  # insert("x~0", x = c("S0_CUM_MET_KRUMBIEGEL1985", "SREL_CUM_MET_KRUMBIEGEL1985"))
  {.}



p_apapbicmet <- P(trafo_apapbicmet)
pars_apapbicmet <- getParameters(p_apapbicmet) %>% are_names_of(0)

p_apapbicmet_sigma_NA <- P(trafo_apapbicmet_sigma_NA)
pars_apapbicmet_sigma_NA <- getParameters(p_apapbicmet_sigma_NA) %>% are_names_of(0)

```

```{r}
data_apapbicmet_sigma_NA %>% select(study, name) %>% unique
```



# dMod.frames

```{r initialize dMod.frames }
basic_hypotheses.frame <- tibble(hypothesis = c("apap",  "bic", "met"),
                     x = list(x_apap,  x_bic, x_met)) %>% 
  add_column( g = list(g_apap,  g_bic, g_met)) %>% 
  add_column(p = list(p_apap,  p_bic, p_met),
             data = list(data_apap,  data_bic, data_met),
             p_sig = list(NULL,  p_bic_sigma_NA, p_met_sigma_NA),
             e = list(NULL,  e_bic_sigma_NA, e_met_sigma_NA),
             data_sig = list(NULL,  data_bic_sigma_NA, data_met_sigma_NA)
  )
# basic_hypotheses.frame <- basic_hypotheses.frame[1,] # keep only apap


bicmet.frame <- tibble(
  hypothesis = "bicmet",
  x = list(x_bicmet),
  g = list(g_bicmet),
  p = list(p_bicmet),
  data = list(data_bicmet),
  p_sig = list(p_bicmet_sigma_NA),
  e = list(e_bicmet),
  data_sig = list(data_bicmet_sigma_NA)
)

apapbicmet.frame <- tibble(
  hypothesis = "apapbicmet",
  x = list(x_apapbicmet),
  g = list(g_apapbicmet),
  p = list(p_apapbicmet),
  data = list(data_apapbicmet),
  p_sig = list(p_apapbicmet_sigma_NA),
  e = list(e_apapbicmet),
  data_sig = list(data_apapbicmet_sigma_NA)
)
```


# Fit

```{r transformation functions for dMod.frame to create objfuns and make the frame smaller again}
dMf_append_objfuns <- function(dMod.frame) dMod.frame %>% 
  
  mutate(data_0 = map(data, as.datalist),
         data_sig = map(data_sig, as.datalist)) %>% 
  mutate(prd_0 = map(seq_along(x), function(i) cfn(g[[i]], cfn(x[[i]],p[[i]]))),
         prd_sig = map(seq_along(x), function(i) cfn(g[[i]], cfn(x[[i]],p_sig[[i]])))) %>% 
  mutate(obj_0 = map(seq_along(x), function(i) normL2(data_0[[i]], prd_0[[i]])),
         obj_sig = map(seq_along(x), function(i) cf_normL2(data = data_sig[[i]], prd_sig[[i]], e = e[[i]]))) %>% 
  
  mutate(obj = map(seq_along(x), function(i) obj_sig[[i]]+obj_0[[i]])) %>% 
  mutate(prd = map(seq_along(x), function(i) prd_sig[[i]]+prd_0[[i]])) %>% 
  mutate(data= map(seq_along(x), function(i) data_sig[[i]]+data_0[[i]])) %>% 
  
  {.}

dMf_reduce <- function(dMod.frame) dMod.frame %>% 
  select(-contains("_0")) %>% 
  select(-contains("_sig"))
```


```{r apply transformations to dMod.frames}
bicmet.frame <- bicmet.frame %>% dMf_append_objfuns 
apapbicmet.frame <- apapbicmet.frame %>% dMf_append_objfuns 
```

```{r test objfuns}
basic_hypotheses.frame %>% dMf_append_objfuns %>% mutate(test = map(seq_along(x), function(i) obj[[i]](getParameters(obj[[i]]) %>% are_names_of(0)))) %>% .$test
bicmet.frame %>% mutate(test = map(seq_along(x), function(i) obj_0[[i]](getParameters(obj[[i]]) %>% are_names_of(0)))) %>% .$test
apapbicmet.frame%>% dMf_reduce() %>%  mutate(test = map(seq_along(x), function(i) obj[[i]](getParameters(obj[[i]]) %>% are_names_of(0)))) %>% .$test
```

```{r}
# save.image(tpaste0("workspace_with_dMod.frames.rda"))
```

# Start fits
```{r load workspace up to here}
load("2018_03_29_20_39_workspace_with_dMod.frames.rda")
rbind(bicmet.frame, apapbicmet.frame) %>% .$x %>% walk(loadDLL)
```

```{r start fits with broad sampling}
# apapbicmet.frame <- apapbicmet.frame %>% dMf_reduce()
# 
# apapbicmet.frame[["pars"]] <- getParameters(apapbicmet.frame[["obj"]][[1]]) %>% are_names_of(0) %>% list
# 
# fit_apapbicmet_broad_sampling <- runbg({
#   ncores <- detectFreeCores()
#   assign("ncores", ncores, pos = .GlobalEnv)
#   
#   apapbicmet.frame %>% 
#     mutate(fits = map(seq_along(x), function(i) {
#       assign("fit_obj", obj[[i]], pos = .GlobalEnv)
#       assign("fit_pars", pars[[i]], pos = .GlobalEnv)
#       assign("fit_studyname", paste0("fits", hypothesis[[i]]), pos = .GlobalEnv)
#       mstrust(objfun = fit_obj, center = fit_pars, studyname = fit_studyname,
#               sd = 4,
#               blather = T, cores = ncores, fits = 10*ncores)
#     }))
#   }, machine = paste0("knecht", 1:5), filename = paste0("tmp_",tpaste0("fit_apapbicmet_broad_sampling")), input = "apapbicmet.frame")
# 
# 
# # ---- start with tight sampling from fitted_pars
# fitted_pars <- readRDS("../fitting/2018_03_29_19_20_fitted_pars_bicmet.rds")$parframes[[1]] %>% as.parvec(1) %>% sort_by_name()
# mypars <- getParameters(apapbicmet.frame[["obj"]][[1]]) %>% are_names_of(0) %>% sort_by_name()
# mypars[names(fitted_pars)] <- fitted_pars
# 
# apapbicmet.frame[["pars"]] <- mypars %>% list
# 
# 
# fit_apapbicmet_tight_sampling_1 <- runbg({
#   ncores <- detectFreeCores()
#   assign("ncores", ncores, pos = .GlobalEnv)
#   
#   apapbicmet.frame %>% 
#     mutate(fits = map(seq_along(x), function(i) {
#       assign("fit_obj", obj[[i]], pos = .GlobalEnv)
#       assign("fit_pars", pars[[i]], pos = .GlobalEnv)
#       assign("fit_studyname", paste0("fits", hypothesis[[i]]), pos = .GlobalEnv)
#       mstrust(objfun = fit_obj, center = fit_pars, studyname = fit_studyname,
#               sd = 0.5,
#               blather = T, cores = ncores, fits = 20*ncores)
#     }))
#   }, machine = paste0("ruprecht", 1), filename = paste0("tmp_",tpaste0("fit_apapbicmet_tight_sampling_1")), input = "apapbicmet.frame")
# 
# # ---- Start with tight sampling around the second best optimum 
# fitted_pars <- readRDS("../fitting/2018_03_29_19_20_fitted_pars_bicmet.rds")$parframes[[1]] %>% as.parvec(3) %>% sort_by_name()
# mypars <- getParameters(apapbicmet.frame[["obj"]][[1]]) %>% are_names_of(0) %>% sort_by_name()
# mypars[names(fitted_pars)] <- fitted_pars
# 
# apapbicmet.frame[["pars"]] <- mypars %>% list
# 
# 
# fit_apapbicmet_tight_sampling_2 <- runbg({
#   ncores <- detectFreeCores()
#   assign("ncores", ncores, pos = .GlobalEnv)
#   
#   apapbicmet.frame %>% 
#     mutate(fits = map(seq_along(x), function(i) {
#       assign("fit_obj", obj[[i]], pos = .GlobalEnv)
#       assign("fit_pars", pars[[i]], pos = .GlobalEnv)
#       assign("fit_studyname", paste0("fits", hypothesis[[i]]), pos = .GlobalEnv)
#       mstrust(objfun = fit_obj, center = fit_pars, studyname = fit_studyname,
#               sd = 0.5,
#               blather = T, cores = ncores, fits = 20*ncores)
#     }))
#   }, machine = paste0("ruprecht", 2), filename = paste0("tmp_",tpaste0("fit_apapbicmet_tight_sampling_2")), input = "apapbicmet.frame")

```

```{r}
# save.image(tpaste0("workspace_apapbicmet_fits_started.rda"))
```

Some comments on the started fits:
    * The objective function is probably not formulated in the most efficient way, I could have defined the observation functions as an addition of individual observation functions
    * I might have been able to merge conditions, but this would have been a hassle
    * the same times being evaluated for each condition is a big minus... (dMod-problem)
    * Maybe compile g and p as well
```{r}
data_apapbicmet %>% 
  rbind(data_apapbicmet_sigma_NA) %>% 
  group_by(study, group) %>% 
  summarise(maxtime = max(time))
```

# Load and look at fits
```{r get fit results from knechte}
# load("2018_03_29_21_15_workspace_apapbicmet_fits_started.rda")
# apapbicmet.frame %>% .$x %>% walk(loadDLL)
# apapbicmet.frame[["fits"]] <- fit_apapbicmet_broad_sampling$get() %>% map("fits") %>% map(1) %>%  Reduce(c.parlist,.) %>% list()
# save.image(tpaste0("workspace_apapbicmet_with_fits.rda"))
```

```{r }
load("2018_03_30_22_51_workspace_apapbicmet_with_fits.rda")
apapbicmet.frame %>% .$x %>% walk(loadDLL)
```

```{r}
apapbicmet.frame <- apapbicmet.frame %>% mutate(prd = map(prd, function(i) {controls(i, name = "attach.input") <- FALSE; i} ))

apapbicmet.frame <- 
  apapbicmet.frame %>% 
  dMf_expand_fits() %>% 
  dMf_append_plots()
```

no nice steps
```{r}
apapbicmet.frame$parframes %>% .[[1]] %>% .[1:100,] %>% plotValues()
```

The error-model just kills the steps, I think. Maybe I should reduce it.
Except for in Krumbiegel, it appears as if the absolute error can be kicked out
```{r}
apapbicmet.frame$parframes %>% .[[1]] %>% .[1:20,] %>% plotPars() +
  coord_cartesian(ylim = c(-5,5))
```

Browsing through the conditions, one can see that met isnt met very well (haha)
```{r}
apapbicmet.frame %>% dMf_append_plots() %>% .[["plot_combined"]]

plotCombined(apapbicmet.frame[["prd"]][[1]](seq(0,24,0.1), 
                                            apapbicmet.frame$best_parvec[[1]], deriv = F),
             apapbicmet.frame[["data"]][[1]], 
             condition %in% rownames(rbind(data_bic_sigma_NA) %>% as.datalist %>% covariates()) &
               name %in% names(observables_bic)#getEquations(apapbicmet.frame[["g"]][[1]])[[1]])
             )
# ggplotly()
```

look at differences in parameters wrt the best parvec
```{r}
myparframe <- apapbicmet.frame$parframes[[1]]

myparframe[,5:27] <- myparframe[,5:27] %>% map(function(i) return(i - i[1]))

myparframe %>% .[1:10,] %>% plotPars() + 
  coord_cartesian(ylim = c(-2,2))
```


found a mistake in the parameter trafos: I didn't rename the error-pars when updating the observables-names












