---
title: "Fitting model 41"
output: 
  html_document:
    toc: TRUE
---


Load all important libraries
```{r setup, message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.height = 10)
knitr::opts_chunk$set(fig.width = 15)
library(dMod)
# library(stringr) # Um bequem mit strings zu arbeiten
# library(tidyverse) # Viele Funktionen, u.a. für data.frames und ggplot2 für schöne plots
# library(magrittr) # der Pipe-operator %>%: z.B: x =" a; y="f(x); z="g(y); wird zu z=" a %>% f %>% g
library(conveniencefunctions)
```


# Read model
```{r}
source("../model/limax_pkpd_v41.R")
```


```{r}
pars_raw <- c(x0, p) 
pars_in_dxdtdmod <- c(getSymbols(dxdt_dmod), names(dxdt_dmod))
```


# Data - read and preprocess
Read data, insert the default values for the parameters supplied in the data sheet. 

* Taheri rausschmeißen zum Fitten: Wird weiter unten getan

```{r, message=FALSE}
data <-
  read_tsv("../data/limax_pkpd_v41_data.csv") %>%
  select(-model) %>% 
  rename(name = observer) %>% 
  rename(n = subjects) %>% 
  unique() #noch matthias sagen, dass lalazar2008 doppelte einträge hat


fitErrorModel_factors <- c("study", "group", "name", "BW", "PODOSE_apap", "IVDOSE_apap", 
"PODOSE_co2c13", "IVDOSE_co2c13", "Ri_co2c13", "ti_co2c13", "PODOSE_metc13", 
"IVDOSE_metc13", "ti_metc13")
some_na <-
  data %>% 
  group_by(study, group, name) %>% 
  mutate(nna = n(), sna = sum(is.na(sigma))) %>% 
  filter(sna>0 & sna != nna) %>% 
  select(-sna, -nna) %>% 
  as.data.frame() %>% 
  fitErrorModel(factors = fitErrorModel_factors, plotting = F, blather = F) 

none_or_all_na <- data %>% 
  group_by(study, group, name) %>% 
  mutate(nna = n(), sna = sum(is.na(sigma))) %>% 
  filter(sna==0 | sna == nna) %>% 
  select(-sna, -nna) %>% 
  as.data.frame()

data <- rbind(some_na, none_or_all_na) %>% 
  select(-n)

supplied_pars <- names(pars_raw)[(names(pars_raw) %in% names(data))]

# data %>% 
#   group_by(study, group, name) %>% 
#   mutate(nna = n(), sna = sum(is.na(sigma))) %>% 
#   filter(!sna == nna) %>% 
#   select(-sna, -nna) %>% 
#   as.data.frame() %>% 
#   fitErrorModel(factors = fitErrorModel_factors, plotting = T, blather = F)
# ggsave("~/Promotion/Writing/Presentations/2018 04 03 Peter Jansen LiSyM/Limax/Errormodels.png")

```

# Set up the model

```{r setup model independently of the individual setups}
# Parameters to fit by Matthias
free_pars_apap <- c("Ka_apap", "APAPD_HLM_CL", "APAPD_Km_apap")
free_pars_bic <- c("Ka_co2c13", "KLU_EXCO2", "CO2FIX_HLM_CL", "KBO_FIXCO2", "KBO_RELCO2", "KBO_MAXCO2")
free_pars_met <- c("Ka_metc13", "CYP1A2MET_CL", "CYP1A2MET_Km_met")

# Observables
observables_apap <- y_dmod[c("Mve_apap")] %>% set_names(c("Mve_apap"))

recovery_bic <- paste(y_dmod["Exhalation_co2c13"], "/ 60 * Mr_co2c13 / Ri_co2c13 * 100")
observables_bic <- c(recovery_bic, y_dmod[c("DOB", "P_CO2Fc13")])
names(observables_bic) <- c("cum_rec_co2c13", "DOB", "P_CO2F")
observables_bic["P_CO2F"] <- paste0(observables_bic["P_CO2F"], " + offset_bic")

recovery_met <- paste(y_dmod["Exhalation_co2c13"], "/ init_PODOSE_metc13 * Mr_metc13 * 100" )
cum_met <- paste( "Abreath_co2c13/ init_PODOSE_metc13 * Mr_metc13 * 100")
observables_met <- c(recovery_met, cum_met) %>% set_names(c("mom_rec_metc13", "cum_rec_metc13"))

# Error models
errors_bic_sigma_NA <- paste0("sqrt(s0_", names(observables_bic), "^2 + srel_", names(observables_bic), "^2 * ", names(observables_bic), "^2 )") %>% set_names(names(observables_bic))
errors_bic_sigma_NA["cum_rec_co2c13"] <- 1 #hierfür gibts eh keine daten und ich weiß nicht, ob ich es einfach weglassen kann

errors_met_sigma_NA <- paste0("sqrt(s0_", names(observables_met), "^2 + srel_", names(observables_met), "^2 * ", names(observables_met), "^2)") %>% set_names(names(observables_met))
errors_met_sigma_NA["mom_rec_metc13"] <- 1 #hierfür gibts eh keine daten mit sigma=NA
```

```{r x, g and e apapbicmet}
free_pars_apapbicmet <- c(free_pars_apap, free_pars_bic, free_pars_met)
odemodel_apapbicmet <- odemodel(dxdt_dmod, modelname = "odemodel_apapbicmet", fixed = setdiff(pars_in_dxdtdmod, c(free_pars_apapbicmet, "Aar_apap"))) # Aar_apap is not there to be optimized, but a variable which is a state is needed because of a bug in odemodel.
x_apapbicmet <- Xs(odemodel_apapbicmet)

g_apapbicmet <- Y(c(observables_apap, observables_bic, observables_met), x_apapbicmet, attach.input = F, modelname = "g_apapbicmet", compile = F)

e_apapbicmet_sigma_NA <- Y(c(errors_bic_sigma_NA, errors_met_sigma_NA), g_apapbicmet)#, modelname = "e_apapbicmet", compile = F) #cant cope with NaNs passed to it, if compiled

pars_errors_apapbicmet <- getSymbols(c(errors_bic_sigma_NA, errors_met_sigma_NA)) %>% str_subset("^s")
```

```{r data and p apapbicmet}
# Split the data in datasets with and without sigma
data_apapbicmet <- data %>% filter(!is.na(sigma)) %>% select(-simulation)
data_apapbicmet_sigma_NA <- data %>% filter(is.na(sigma)) %>% select(-simulation)

# Get all parameters that in some way replace pars_raw (parameters supplied by the SBML file) or are additional parameters that we need to fit
# This could be e.g. Study specific pars such as IVDOSE* or pars that are fitted
outer_pars_apapbicmet <- sort(unique(c(free_pars_apapbicmet, supplied_pars)))
outer_pars_apapbicmet_sigma_NA <- sort(unique(c(outer_pars_apapbicmet, pars_errors_apapbicmet)))

# Define the parameter trafos which in turn define the different conditions
trafo_apapbicmet<-
  c(pars_raw) %>% 
  sort_by_name() %>% 
  replace(names(.) %in% outer_pars_apapbicmet, outer_pars_apapbicmet) %>% 
  
  branch(data_apapbicmet %>% as.datalist() %>% covariates()) %>% # The table of covariates includes dosepar and dose, which are used in the next line
  
  insert("name ~ value", value = unlist(mget(supplied_pars)), name = supplied_pars) %>% 

  define("init_PODOSE_metc13~podose", podose = mytrafo[[i]]["PODOSE_metc13"]) %>% # For the observables, I need the initial dose as a fixed parameter which doesn't change. Because the PODOSE_metc13 is also a state, I need to duplicate this parameters
  
  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) %>% 
  
  define("x~x", x = "offset_bic")


trafo_apapbicmet_sigma_NA <-
  c(pars_raw, pars_errors_apapbicmet) %>% 
  sort_by_name() %>% 
  replace(names(.) %in% outer_pars_apapbicmet_sigma_NA, outer_pars_apapbicmet_sigma_NA) %>% 
  
  branch(data_apapbicmet_sigma_NA %>% as.datalist() %>% covariates()) %>% # The table of covariates includes dosepar and dose, which are used in the next line
  insert("name ~ value", value = unlist(mget(supplied_pars)), name = supplied_pars) %>% 
  #bic

  #met
  define("init_PODOSE_metc13~podose", podose = mytrafo[[i]]["PODOSE_metc13"]) %>% # For the observables, I need the initial dose as a fixed parameter which doesn't change. Because the PODOSE_metc13 is also a state, I need to duplicate this parameters
  
  insert("x~exp(X)", x = getSymbols(mytrafo[[i]]), X = toupper(getSymbols(mytrafo[[i]]))) %>% 
  
  #bic
  define("x~x", x = "offset_bic") %>% 
  
  #met
  {.}



p_apapbicmet <- P(trafo_apapbicmet, modelname = "p_apapbicmet", compile = F)
pars_apapbicmet <- getParameters(p_apapbicmet) %>% are_names_of(0)

p_apapbicmet_sigma_NA <- P(trafo_apapbicmet_sigma_NA, modelname = "p_sig_apapbicmet", compile = F)

pars_apapbicmet_sigma_NA <- getParameters(p_apapbicmet_sigma_NA) %>% are_names_of(0)


compile(g_apapbicmet,  p_apapbicmet, p_apapbicmet_sigma_NA, cores = 3, output = "apapbicmet")
```


# dMod.frames

```{r initialize dMod.frames }
apapbicmet.frame <- dMod.frame(
  hypothesis = "apapbicmet",
  x = x_apapbicmet,
  g = g_apapbicmet,
  p = p_apapbicmet,
  data = data_apapbicmet,
  e = NULL,
  x_sig = list(x_apapbicmet),
  g_sig = list(g_apapbicmet),
  p_sig = list(p_apapbicmet_sigma_NA),
  e_sig = list(e_apapbicmet_sigma_NA),
  data_sig = as.datalist(data_apapbicmet_sigma_NA)
)



```


# Prepare fits

```{r functions for dMod.frames to create objfuns and make them frame smaller again}
dMf_append_objfuns <- function(dMod.frame) dMod.frame %>% 
    mutate(data_0 = map(data_0, as.datalist),
         data_sig = map(data_sig, as.datalist)) %>% 
  mutate(prd_0 = map(seq_along(x), function(i) cfn(g[[i]], cfn(x[[i]],p_0[[i]]))),
         prd_sig = map(seq_along(x), function(i) cfn(g[[i]], cfn(x[[i]],p_sig[[i]])))) %>% 
  mutate(obj_0 = map(seq_along(x), function(i) normL2(data_0[[i]], prd_0[[i]])),
         obj_sig = map(seq_along(x), function(i) cf_normL2(data = data_sig[[i]], prd_sig[[i]], e = e[[i]]))) %>% 
  
  mutate(obj = map(seq_along(x), function(i) obj_sig[[i]]+obj_0[[i]])) %>% 
  mutate(prd = map(seq_along(x), function(i) prd_sig[[i]]+prd_0[[i]])) %>% 
  mutate(data= map(seq_along(x), function(i) data_sig[[i]]+data_0[[i]])) 

dMf_reduce <- function(dMod.frame) dMod.frame %>% 
  select(-contains("_0")) %>% 
  select(-contains("_sig"))
```

```{r augment dMod.frames}
basic_hypotheses.frame <- basic_hypotheses.frame %>% 
  dMf_append_objfuns()
  
bicmet.frame <- bicmet.frame%>% 
  dMf_append_objfuns()

apapbicmet.frame <- apapbicmet.frame%>% 
  dMf_append_objfuns()
```


```{r test objfuns}
basic_hypotheses.frame %>% .$obj %>% walk(loadDLL)
bicmet.frame %>% .$obj %>% walk(loadDLL)
apapbicmet.frame %>% .$obj %>% walk(loadDLL)


# basic_hypotheses.frame %>% mutate(test = map(seq_along(x), function(i) {
#   return(obj[[i]](getParameters(obj[[i]]) %>% are_names_of(0)))})
#   ) %>% .$test

bicmet.frame %>% mutate(test = map(seq_along(x), function(i) obj_sig[[i]](getParameters(obj_sig[[i]]) %>% are_names_of(0)))) %>% .$test

apapbicmet.frame%>% dMf_reduce() %>%  mutate(test = map(seq_along(x), function(i) obj[[i]](getParameters(obj[[i]]) %>% are_names_of(0)))) %>% .$test



```


```{r}
save.image(tpaste0("workspace_with_dMod.frames.rda"))
```



# Fit with prior around pars_raw, srel = -1, s0 = -2
```{r, dependson="setup"}
# load("2018_04_23_16_57_workspace_with_dMod.frames.rda")
# apapbicmet.frame %>% .$obj %>% walk(loadDLL)
```

```{r fix errorpars}
# s0 <- paste(c("S0"), c("CUM_REC_METC13", "DOB", "P_CO2F"), sep = "_")
# srel <- paste(c("SREL"), c("CUM_REC_METC13", "DOB", "P_CO2F"), sep = "_")
# trafo_sigma_set <- trafo_apapbicmet_sigma_NA %>% 
#   insert("x~-1", x = srel) %>% 
#   insert("x~-2", x = s0)
# 
# p_sig <- P(trafo_sigma_set, modelname = "p_apapbicmet_sigma_set", compile = F)
# compile(p_sig, output = "p_apapbicmet_sigma_set")
# ```
# 
# ```{r setup prior}
# getParameters(p_sig)
# 
# myindices <- pars_raw %>% names %>% toupper() %>% {which(. %in% getParameters(p_sig))}
# 
# prior_mu <- log(pars_raw[myindices])
# names(prior_mu) <- toupper(names(prior_mu))

```

```{r setup prior.frame}
# prior.frame <- apapbicmet.frame
# prior.frame[["hypothesis"]] <- "srel = -1,s0=-2, prior_sigma ="
# 
# prior.frame[["p_sig"]] <- list(p_sig)
# 
# prior.frame <- prior.frame %>% 
#   mutate(data_0 = map(data_0, . %>% 
#                         .[!((names(.) %>% str_detect("lbert")) & (names(.) %>% str_detect("caps")))] %>% 
#                         .[!(names(.) %>% str_detect("Mohr"))])) %>% 
#   mutate(prd_0 = map(seq_along(x), function(i) cfn(g[[i]], cfn(x[[i]],p_0[[i]]))),
#          prd_sig = map(seq_along(x), function(i) cfn(g[[i]], cfn(x[[i]],p_sig[[i]])))) %>% 
#   mutate(obj_0 = map(seq_along(x), function(i) normL2(data_0[[i]], prd_0[[i]])),
#          obj_sig = map(seq_along(x), function(i) cf_normL2(data = data_sig[[i]], prd_sig[[i]], e = e[[i]]))) %>% 
#   
#   mutate(obj = map(seq_along(x), function(i) obj_sig[[i]]+obj_0[[i]])) %>% 
#   mutate(prd = map(seq_along(x), function(i) prd_sig[[i]]+prd_0[[i]])) %>% 
#   mutate(data= map(seq_along(x), function(i) data_sig[[i]]+data_0[[i]])) 
#   
# 
# prior.frame <- rbind(prior.frame, prior.frame, prior.frame, prior.frame) %>% 
#   mutate(obj_data = obj) %>% 
#   mutate(constr = map(seq_along(x), function(i) {
#     {constraintL2(prior_mu, sigma = 10^(i-4))}
#   })) %>% 
#   mutate(obj = map(seq_along(x), function(i) {
#     obj_data[[i]]+constr[[i]]
#   })) %>% 
#   mutate(hypothesis = map_chr(1:4, function(i) paste0(hypothesis[i], 10^(i-4))))
# prior.frame[["pars"]] <- map(1:4, function(i) c(prior_mu, offset_bic = -0.011))
```

```{r test objfn}
# prior.frame %>% mutate(test = map(seq_along(x), function(i) getParameters(obj[[i]]))) %>% .$test

# # prior.frame %>% mutate(test = map(seq_along(x), function(i) obj[[i]](getParameters(obj[[i]]) %>% are_names_of(0)))) %>% .$test
# prior.frame %>% mutate(test = map(seq_along(x), function(i)  obj[[i]](pars[[i]]))) %>% .$test %>% page
# 
# prior.frame %>% mutate(test = map(seq_along(x), function(i)  obj_data[[i]](pars[[i]]))) %>% .$test %>% page
# 
# prior.frame %>% mutate(test = map(seq_along(x), function(i)  constr[[i]](pars[[i]]))) %>% .$test %>% page

```

```{r start and retrieve fits}
# fit_with_prior <- runbg({
#   ncores <- detectFreeCores()
#   assign("ncores", ncores, pos = .GlobalEnv)
# 
#   prior.frame %>%
#     
#     mutate(fits = map(seq_along(x), function(i) {
#       assign("fit_obj", obj[[i]], pos = .GlobalEnv)
#       assign("fit_pars", pars[[i]], pos = .GlobalEnv)
#       assign("fit_studyname", paste0("fits", hypothesis[[i]]), pos = .GlobalEnv)
#       mstrust(objfun = fit_obj, center = fit_pars, studyname = fit_studyname,
#               sd = 3,
#               blather = F, cores = ncores, fits = 10*ncores)
#     }))
#   }, machine = paste0("knecht", 1:5), filename = paste0("tmp_",tpaste0("fit_with_prior")), input = "prior.frame")
# 
# saveRDS(fit_with_prior, tpaste0("fit_with_prior.rds"))
# fit_with_prior <- fit_with_prior$get()
# myfits <- fit_with_prior %>% map("fits") %>% .[c(1,2,3,5)] %>% transpose() %>% map(. %>% Reduce(c.parlist,.))
# prior.frame[["fits"]] <- myfits
# saveRDS(prior.frame, tpaste0("prior.frame.rds")) # "2018_04_02_22_37_prior.frame.rds"
# 
# prior.frame <- readRDS("2018_04_02_22_37_prior.frame.rds")
# ```
# 
# ```{r}
# prior.frame <- prior.frame %>% dMf_expand_fits() %>% dMf_append_plots()
# ```
# 
# ```{r}
# prior.frame$plot_value
# prior.frame$parframes %>% map(. %>% .[1:600]) %>% map(plotValues,tol = 10)
# ```
# 
# ```{r}
# prior.frame %>% dMf_append_plots(tol  = 10, name %in% names(observables_bic)&(condition %in% names(rbind(data_bic,data_bic_sigma_NA) %>% as.datalist))) %>% .$plot_combined
```

## Run profiles for the prior.frame

```{r start and retrieve profiles for prior.frame}
# profile_jobs_prior <- map(1:4, function(j) {
#   assign("myframe",  prior.frame[j,], pos = .GlobalEnv)
#   runbg({
#     ncores <- detectFreeCores()
#     assign("ncores", ncores, pos = .GlobalEnv)
#     
#     myframe %>%
#       mutate(profiles = map(seq_along(x), function(i) {
#         assign("fit_obj", obj[[i]], pos = .GlobalEnv)
#         assign("fit_pars", best_parvec[[i]], pos = .GlobalEnv)
#         
#         profile(obj = fit_obj, pars = fit_pars, whichPar = names(fit_pars), cores = ncores)
#       }))
#   }, machine = paste0("knecht", c(j)), filename = paste0("tmp_",tpaste0("profile_jobs_prior")), input = "myframe")
# })
# 
#  saveRDS(profile_jobs_prior, tpaste0("profile_jobs_prior.rds"))
# profile_jobs_prior <- readRDS("2018_04_02_23_22_profile_jobs_prior.rds")
# prior.frame <- profile_jobs_prior %>% map(. %>% {.$get()} %>% .[[1]]) %>% do.call(rbind,.)
# saveRDS(prior.frame %>% shrink_fits() %>% shrink_plots(), tpaste0("prior.frame_with_profiles.rds")) # "2018_04_06_13_50_prior.frame_with_profiles.rds"
# prior.frame <- readRDS("2018_04_06_13_50_prior.frame_with_profiles.rds")
```



Looking at the profiles, some of the parameters are really far off their original values, whereas many can be determined quite well from the data.

Prior were good guesses for
  KA_APAP, offset_bic

APAPD_HLM_CL, APAPD_KM_APAP, CO2FIX_HLM_CL, CYP1A2MET_CL, 
    CYP1A2MET_KM_MET, , KA_CO2C13, KA_METC13, KBO_FIXCO2, 
    KBO_MAXCO2, KBO_RELCO2, KLU_EXCO2, offset_bic

I think, data is contributing enough for the following parameters, so the prior is not needed for them anymore
  APAPD_HLM_CL, APAPD_KM_APAP, KA_APAP



```{r}
# prior.frame$obj[[1]] %>% getParameters() %>% map(as.name) %>% unlist %>% dput
```


```{r}
# prior.frame$profiles %>% 
#   plotProfile() + 
#   coord_cartesian(ylim = c(-2, 4))
```

No comment on the paths yet.
```{r}
# prior.frame$profiles %>% plotPaths(whichPar = "KBO_FIXCO2")
```

The plotCombined looks much better with weaker priors!
```{r}
# prior.frame$obj %>% walk(loadDLL)
# prior.frame %>% plotCombined.dMod.frame(hypothesis = 4)
# map(1:4, . %>% plotCombined.dMod.frame(prior.frame, hypothesis = .))
```


# Run one fit with weak prior
```{r, dependson="setup"}
# load("2018_03_31_02_21_workspace_with_dMod.frames.rda")
# 
# rbind(bicmet.frame, apapbicmet.frame) %>% .$obj %>% walk(loadDLL)
```


```{r setup prior.frame_weak}
# prior.frame_weak <- apapbicmet.frame
# prior.frame_weak[["hypothesis"]] <- "srel = -1,s0=-2, prior_sigma ="
# 
# prior.frame_weak[["p_sig"]] <- list(p_sig)
# 
# prior.frame_weak <- prior.frame_weak %>%
#   mutate(data_0 = map(data_0, . %>%
#                         .[!((names(.) %>% str_detect("lbert")) & (names(.) %>% str_detect("caps")))] %>%
#                         .[!(names(.) %>% str_detect("Mohr"))])) %>%
#   mutate(prd_0 = map(seq_along(x), function(i) cfn(g[[i]], cfn(x[[i]],p_0[[i]]))),
#          prd_sig = map(seq_along(x), function(i) cfn(g[[i]], cfn(x[[i]],p_sig[[i]])))) %>%
#   mutate(obj_0 = map(seq_along(x), function(i) normL2(data_0[[i]], prd_0[[i]])),
#          obj_sig = map(seq_along(x), function(i) cf_normL2(data = data_sig[[i]], prd_sig[[i]], e = e[[i]]))) %>%
# 
#   mutate(obj = map(seq_along(x), function(i) obj_sig[[i]]+obj_0[[i]])) %>%
#   mutate(prd = map(seq_along(x), function(i) prd_sig[[i]]+prd_0[[i]])) %>%
#   mutate(data= map(seq_along(x), function(i) data_sig[[i]]+data_0[[i]]))
# 
# 
# prior.frame_weak <- rbind(prior.frame_weak, prior.frame_weak) %>%
#   mutate(obj_data = obj) %>%
#   mutate(constr = map(seq_along(x), function(i) {
#     {constraintL2(prior_mu, sigma = i*5)}
#   })) %>%
#   mutate(obj = map(seq_along(x), function(i) {
#     obj_data[[i]]+constr[[i]]
#   })) %>%
#   mutate(hypothesis = map_chr(c(1:2), function(i) paste0(hypothesis[i], i*5)))
# prior.frame_weak[["pars"]] <- map(1:2, function(i) c(prior_mu, offset_bic = -0.011))
```

```{r fit and profiles weak prior}
# fit_with_weaker_prior <- runbg({
#   ncores <- detectFreeCores()
#   assign("ncores", ncores, pos = .GlobalEnv)
#   
#   prior.frame_weak %>% 
#   mutate(fits = map(seq_along(x), function(i) {
#     assign("fit_obj", obj[[i]], pos = .GlobalEnv)
#     assign("fit_pars", pars[[i]], pos = .GlobalEnv)
#     assign("fit_studyname", paste0("fits", hypothesis[[i]]), pos = .GlobalEnv)
#     mstrust(objfun = fit_obj, center = fit_pars, studyname = fit_studyname,
#             sd = 3,
#             blather = F, cores = ncores, fits = 10*ncores)
#   }))
# },  machine = c(paste0("knecht", 3:4), paste0("ruprecht",1:2)), input = "prior.frame_weak", filename = "2018_04_12_18_28_fit_with_weaker_prior_runbg")
# saveRDS(fit_with_weaker_prior, file = "2018_04_12_18_28_fit_with_weaker_prior.rds")
# fit_with_weaker_prior <- readRDS("2018_04_12_18_28_fit_with_weaker_prior.rds")
# fit_with_weaker_prior$check()
# wait_for_runbg(fit_with_weaker_prior)
# fit_with_weaker_prior_results <- fit_with_weaker_prior$get()
# saveRDS(fit_with_weaker_prior_results, file = "2018_04_12_18_28_fit_with_weaker_prior_results.rds")
# fit_with_weaker_prior$purge()


# fit_with_weaker_prior <- readRDS("2018_04_12_18_28_fit_with_weaker_prior_results.rds")
# ```
# 
# ```{r}
# myfits <-
#   map(fit_with_weaker_prior, "fits") %>% 
#   transpose() %>% 
#   map(. %>% Reduce(c.parlist,.)) 
# prior.frame_weak <- fit_with_weaker_prior[[1]]
# prior.frame_weak$fits <- myfits
# ```
# 
# 
# ```{r}
# prior.frame_weak$obj %>% walk(loadDLL)
# prior.frame_weak <- prior.frame_weak %>% dMf_expand_fits() #%>% dMf_append_plots(index = 1:400)
# 
# prior.frame$obj %>% walk(loadDLL)
# prior.frame$prd <- map(1:4, function(i) prior.frame_weak$prd[[1]])
# prior.frame <- prior.frame %>% dMf_expand_fits() %>% dMf_append_plots()
# 
# ```
# 
# Seems as if there are some decent steps this time
# ```{r}
# prior.frame$plot_value
# prior.frame_weak %>% str1
# ```
# 

# ## profiles with weak prior
# ```{r}
# profiles_weak_prior_job <- runbg({
#     ncores <- detectFreeCores()
#     assign("ncores", ncores, pos = .GlobalEnv)
#   
#   prior.frame_weak %>%
#     mutate(profiles = map(seq_along(x), function(i) {
#       assign("fit_obj", obj[[i]], pos = .GlobalEnv)
#       assign("fit_pars", best_parvec[[i]], pos = .GlobalEnv)
#       
#       profile(obj = fit_obj, pars = fit_pars, whichPar = names(fit_pars), cores = ncores)
#     }))
# },  machine = c(paste0("ruprecht", 1)), input = "prior.frame_weak", filename = "2018_04_13_12_56_profiles_weak_prior_job_runbg")
# saveRDS(profiles_weak_prior_job, file = "2018_04_13_12_56_profiles_weak_prior_job.rds")
# profiles_weak_prior_job <- readRDS("2018_04_13_12_56_profiles_weak_prior_job.rds")
# profiles_weak_prior_job$check()
# wait_for_runbg(profiles_weak_prior_job, delta_t = 60)
# beepr::beep()
# profiles_weak_prior_job_results <- profiles_weak_prior_job$get()
# saveRDS(profiles_weak_prior_job_results, file = "2018_04_13_12_56_profiles_weak_prior_job_results.rds")
# profiles_weak_prior_job$purge()
# prior.frame_weak <- readRDS("2018_04_13_12_56_profiles_weak_prior_job_results.rds")$ruprecht1
```



# Reconcile fit results with new .c-files
I had the trouble that there was a random string attached to the function names in the .c-files, so when I let the script run again, these changed and the saved objects couldn't find their functions anymore in the DLLs. This is now fixed
```{r}
# prior.frame_old <- readRDS("2018_04_06_13_50_prior.frame_with_profiles.rds")
# prior.frame <- prior.frame %>%
#   add_column(parframes = prior.frame_old$parframes,
#              profiles = prior.frame_old$profiles)
# 
# prior.frame_weak_old <- readRDS("2018_04_13_12_56_profiles_weak_prior_job_results.rds")$ruprecht1
# prior.frame_weak <- prior.frame_weak %>%
#   add_column(parframes = prior.frame_weak_old$parframes,
#     profiles = prior.frame_weak_old$profiles)
# 
# saveRDS(rbind(prior.frame, prior.frame_weak), file = tpaste0("prior.frame_full.rds"))
# prior.frame <- readRDS("2018_04_23_17_00_prior.frame_full.rds")

```


# Look at results
```{r}
prior.frame <- readRDS("2018_04_23_17_00_prior.frame_full.rds")
prior.frame$obj %>% walk(loadDLL)
```


The profiles of the fits with weak prior are really bad and again slip into the trap with CYP1A2MET_KM_MET going to zero.
This again results in the profiles being wiggly and not reaching the limits.
Description of the profiles and further thoughts:
* Profiles for which I think the prior can definitely be removed:
    1. APAPD_HLM_CL
    1. APAP_KM_APAP
    1. KLU_EXCO2C13
```{r}
prior.frame$profiles %>% 
  plotProfile() +
  coord_cartesian(ylim = c(-2, 4)) +
  # scale_color_brewer() +
  geom_blank()
# ggplotly()
```


## Question: Which conditions push the parameter CYP1A2MET_KM_MET to -Inf?
```{r}
prior.frame <-
  prior.frame %>% 
  rowwise() %>% 
  mutate(condwise_data = list(obj_condition_wise(obj_data, parframes %>% as.parvec)),
         condwise_sum = list(obj_condition_wise(obj, parframes %>% as.parvec)),
         condwise_constr = list(obj_condition_wise(constr, parframes %>% as.parvec)))
```

Look at the conditions in hypothesis 4
```{r}
unnest_name <- function(myframe, unique = "condition", unnest_var = "gradient") {
  myframe_2 <- myframe %>% .[c(unique, unnest_var)]
  myframe_2 <- myframe_2 %>% apply(1, function(i) {
    tibble(condition = i[[unique]], grad_value = unlist(i[[unnest_var]]), grad_name = unlist(names(i[[unnest_var]])))
  }) %>% do.call(rbind,.)
  
  left_join(myframe, myframe_2)
}

prior.frame$condwise_data[[4]] %>% 
  do.call(rbind,.) %>% 
  unnest_name() %>% 
  ggplot(aes(y = grad_name, x = grad_value, color = condition)) + 
  geom_point()

# ggplotly()


git_add_dMod.frame("2018_04_23_17_00_prior.frame_full.rds")

```

```{r}
prior.frame$condwise_data[[4]] %>% 
  do.call(rbind,.) %>% 
  unnest_name() %>% 
  group_by(grad_name) %>%
  mutate(sum_val = sum(grad_value)) %>% 
  ggplot(aes(y = grad_name, x = sum_val, color = condition)) + 
  geom_point()
```

```{r}
prior.frame$condwise_sum[[4]] %>% 
  do.call(rbind,.) %>% 
  unnest_name() %>% 
  group_by(grad_name) %>%
  mutate(sum_val = sum(grad_value)) %>% 
  arrange(desc(sum_val), grad_name)
  ggplot(aes(y = grad_name, x = sum_val, color = condition)) + 
  geom_point() 
```

```{r}
prior.frame <- prior.frame %>% 
  mutate(val_sum = list(obj(parframes %>% as.parvec)),
         val_data = list(obj_data(parframes %>% as.parvec)),
         val_constr = list(constr(parframes %>% as.parvec)))
```

```{r}
prior.frame$val_sum[[4]]$gradient
```


```{r}
# myframe <- prior.frame$condwise[[4]] %>% 
#   do.call(rbind,.) 


unnest_name(myframe) %>% print


```
















