---
title: "Fitting LiMAx model"
output: 
  html_document:
    toc: TRUE
---

Load required libraries
```{r, message=FALSE, warning=FALSE, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.height = 10)
knitr::opts_chunk$set(fig.width = 15)
library(dMod)
library(stringr) # Um bequem mit strings zu arbeiten
library(tidyverse) # Viele Funktionen, u.a. für data.frames und ggplot2 für schöne plots
library(magrittr) # der Pipe-operator %>%: z.B: x =" a; y="f(x); z="g(y); wird zu z=" a %>% f %>% g
library(conveniencefunctions)
```

```{r load old workspace, eval=TRUE}
# load("2018-03-01 16-10 workspace.rda")
```

# Read model
SBML model was converted to R code for model fitting
```{r}
source("../model/limax_pkpd_39.R")
```

Reading parameters and setting fitting parameters
```{r}
pars <- c(x0, p)
pars_to_optimize <- c("Ka_apap", "APAPD_HLM_CL", "APAPD_Km_apap") 

# get all parameters occuring in dxdt_dmod
pars_in_dxdtdmod <- c(getSymbols(dxdt_dmod), names(dxdt_dmod))
```

## parameters occuring in the ode, but not in "pars"
```{r}
setdiff(pars_in_dxdtdmod, names(pars))
```

## parameters occuring in "pars", but not in the ode
```{r}
setdiff(names(pars), pars_in_dxdtdmod) 
```

## ODE model and prediction function
dMod model definition
```{r, eval=TRUE}
myodemodel <- odemodel(dxdt_dmod, fixed = setdiff(pars_in_dxdtdmod, c(pars_to_optimize, "Aar_apap"))) 
# Aar_apap is not there to be optimized, but a variable which is a state is needed because of a bug in odemodel.

saveRDS(myodemodel, "odemodel.rds")
modemodel <- readRDS("odemodel.rds")
x <- Xs(myodemodel)
loadDLL(x)
```

## Observation function
```{r}
observables <- y_dmod[c("Mve_apap", "DOB")] %>% set_names(c("apap", "dob"))

g <- Y(observables, x)
```

## Data
Read and transform to dMod-style
```{r}
files <- file.path("../data", list.files("../data", pattern = ".csv", recursive = T))

data_0 <- lapply(files, . %>% read_tsv) %>% do.call(dMod::combine,.)

data_0 <- data_0 %>% 
  mutate(apap_se = apap_sd/sqrt(n)) %>% 
  mutate(name = "apap") %>% 
  
  mutate(dose = replace(dose, is.na(dose), "")) %>% 
  mutate(route = replace(route, is.na(route), "")) %>% 
  mutate(application = replace(application, str_detect(application, "capsule"), "capsule"),
         application = replace(application, is.na(application), "")) %>% 
  
  unite("study", study, application, route, dose, sep = "") %>% 
  
  select(study, n, name, time, value = apap, sigma = apap_se) %>% 
  filter(!is.na(value)) %>% 
  {.}

data_0 <- fitErrorModel(data_0, factors = c("study"))

doses <- tibble(study =  unique(data_0$study), 
                dose = c(650, 650, 1500,5600,1400,1000,1000,2000,500),
                dosepar = c(rep("PODOSE_apap", 5), "IVDOSE_apap", rep("PODOSE_apap", 3)))


data_0 <- full_join(data_0, doses)
data_0 <-  data_0 %>% select(-n)
```


## Prepare conditions
```{r}
covtable <- data_0 %>% as.datalist() %>% covariates()

dosepars <- doses$dosepar %>% unique
outer_pars <- sort(c(dosepars, pars_to_optimize))

trafo <-
  pars %>% 
  sort_by_name() %>% 
  replace((names(.) %in% outer_pars), outer_pars) %>% 
  branch(covtable) %>% 
  define("dosepar~dose", dosepar = dosepar, dose = dose) %>% #insert values for the doses
  insert("remainingdosepar~0", remainingdosepar = dosepars) %>% 
  insert("x~exp(X)", x = pars_to_optimize, X = toupper(pars_to_optimize)) 

p_0 <- P(trafo)

mypars <- log(pars[pars_to_optimize]) %>% set_names(toupper(pars_to_optimize))

```

### Plot
```{r, eval=TRUE}
times <- seq(0,24, 0.1)
plotCombined((g*x*p_0)(times, mypars, deriv = F), data = data_0 %>% as.datalist, name %in% names(observables))
```


## Fit
```{r}
obj <- normL2(data_0 %>% as.datalist, (g*x*p_0))

# sampling (sd on top of the log transformed parameters)
myfits_0 <- mstrust(obj, mypars, "first_fits", result_path = "intermediate_results", sd = 5, fits = 10, cores = 12, blather = T)
```

List the fit results
```{r, eval=TRUE}
myfits_0%>% as.parframe()%>% head(20)
```

Running the fit as a background process or on other machines:


```{r}
out_job2 <- runbg({mstrust(obj, mypars, "test_fits", result_path = "test_fits", sd = 5, fits = 50, cores = detectFreeCores(), blather = T)}, machine = c("trip1", "trip2"))
# How to abort jobs in the background?
```

```{r}
ready = F
while (ready == F){
  ready = out_job2$check()
  Sys.sleep(5)
}

# Retrieve fit results from the background process.
out_job2$get()
myfits_2 <- .runbgOutput

myfits_2$trip1 %>% as.parframe()%>% head(20)
myfits_2$trip2 %>% as.parframe()%>% head(20)
out_job2$purge()
```


### Plot the best fit
```{r, eval=TRUE}
myfits_0 %>% as.parframe() %>% as.parvec()
plotCombined((g*x*p_0)(times, myfits_0 %>% as.parframe() %>% as.parvec(), deriv = F), data = data_0 %>% as.datalist, name %in% c("apap")) + 
  ggtitle(paste("           -2LL =", myfits_0 %>% as.parframe() %>% .[1,"value"] %>% unlist %>% round(2)))
```

To me it looks as if the data of Albert1974 capsule is shifted to the right, since its rise starts later.
In the end this makes sense, because the capsule first needs to burst. The question is, how do we deal with this?


# Allow for different Aborption speeds

To me it looks as if the data of Albert1974 capsule is shifted to the right, since its rise starts later.
In the end this makes sense, because the capsule first needs to burst. The question is, how do we deal with this?

In a first step, let's assume all studies have a different absorption rate Ka_apap.


## Data
Read and transform to dMod-style
```{r}
files <- file.path("../data", list.files("../data", pattern = ".csv", recursive = T))

data_1 <- lapply(files, . %>% read_tsv) %>% do.call(dMod::combine,.)

data_1 <- data_1 %>% 
  mutate(apap_se = apap_sd/sqrt(n)) %>% 
  mutate(name = "apap") %>% 
  
  mutate(dose = replace(dose, is.na(dose), "")) %>%
  mutate(route = replace(route, is.na(route), "")) %>% 
  mutate(application = replace(application, str_detect(application, "capsule"), "capsule"),
         application = replace(application, is.na(application), "")) %>% 
  
  # unite("study", study, application, route, dose, sep = "") %>% 
  
  select(study, application, route, dose, n, name, time, value = apap, sigma = apap_se) %>% 
  filter(!is.na(value)) %>% 
  {.}

data_1 <- fitErrorModel(data_1, factors = c("study", "application", "route", "dose"), plotting = F)

plotData(as.datalist(data_1))


doses <- data.frame(unique(data_1[c("study", "application", "route", "dose")])[-4] %>% as.list, 
                dose = as.character(c(650, 650, 1500,5600,1400,1000,1000,2000,500)),
                dosepar = c(rep("PODOSE_apap", 5), "IVDOSE_apap", rep("PODOSE_apap", 3)),
                stringsAsFactors = F)


data_1

data_1 <-
  rbind(
  left_join(data_1 %>% select(-dose), doses) %>% filter(!str_detect(study, "Rawlins1977")), 
  right_join(data_1, doses) %>% filter(!is.na(value))
)
data_1 <-  data_1 %>% select(-n)

plotData(as.datalist(data_1))
```



## Prepare conditions
```{r}
covtable <- data_1 %>% as.datalist() %>% covariates()

dosepars <- doses$dosepar %>% unique

outer_pars <- sort(c(dosepars, pars_to_optimize))


trafo <-
  pars %>% 
  sort_by_name() %>% 
  replace((names(.) %in% outer_pars), outer_pars) %>% 
  branch(covtable) %>% 
  define("dosepar~dose", dosepar = dosepar, dose = dose) %>% #insert values for the doses
  insert("remainingdosepar~0", remainingdosepar = dosepars) %>% # replace the other dose_par by zero
  
  insert("x~x_study_application", x = "Ka_apap", study = study, application = application) %>% 
  
  # insert("x~exp(X)", x = pars_to_optimize, X = toupper(pars_to_optimize)) 
  insert("x~exp(X)", x = mytrafo[[i]][is.na(as.numeric(mytrafo[[i]]))], X = toupper(mytrafo[[i]][is.na(as.numeric(mytrafo[[i]]))]))  # hacking insert()...

## trafo %>% head(1)
p_1 <- P(trafo)



mypars_1 <- getParameters(p_1) %>% are_names_of(0)


dxdt_dmod %>% .[str_detect(.,"Km_apap")]

```



## Fit
```{r}
obj <- normL2(data_1 %>% as.datalist, (g*x*p_1))

myfits_1 <- mstrust(obj, mypars_1, "second_fits", result_path = "intermediate_results", sd = 5, fits = 20, cores = 4, blather = T)
```

Show which fits converged
```{r, eval=TRUE}
myfits_1 %>% as.parframe() %>% head(7)
```

### Plot the best fit
Making the Ka_apap parameters condition specific improves the fit.
```{r, eval=TRUE}
plotCombined((g*x*p_1)(times, myfits_1 %>% as.parframe() %>% as.parvec(1), deriv = F), data = data_1 %>% as.datalist, name %in% c("apap")) + 
  ggtitle(paste("           -2LL =", myfits_1 %>% as.parframe() %>% .[1,"value"] %>% unlist %>% round(2)))
# plotly::ggplotly()
```




# Allow for different doses

It seems as if the specified dosing is too low in many cases. Therefore, we should try to adjust the dosing. This might help to account for the different bodyweights, different absorption efficiencies, etc...


## Prediction function with sensitivites also for doses
```{r}
# myodemodel_2 <- odemodel(dxdt_dmod, fixed = setdiff(pars_in_dxdtdmod, c(pars_to_optimize, "Aar_apap", "PODOSE_apap", "IVDOSE_apap")), modelname = "odemodel_2") # Aar_apap is not there to be optimized, but a variable which is a state is needed because of a bug in odemodel.
# saveRDS(myodemodel_2, "odemodel_2.rds")
myodemodel_2 <- readRDS("odemodel_2.rds")
x_2 <- Xs(myodemodel_2)
loadDLL(x_2)
```



## Data
Read and transform to dMod-style
```{r}
files <- file.path("../data", list.files("../data", pattern = ".csv", recursive = T))

data_2 <- lapply(files, . %>% read_tsv) %>% do.call(dMod::combine,.)

data_2 <- data_2 %>% 
  mutate(apap_se = apap_sd/sqrt(n)) %>% 
  mutate(name = "apap") %>% 
  
  mutate(dose = replace(dose, is.na(dose), "")) %>%
  mutate(route = replace(route, is.na(route), "")) %>% 
  mutate(application = replace(application, str_detect(application, "capsule"), "capsule"),
         application = replace(application, is.na(application), "")) %>% 
  
  # unite("study", study, application, route, dose, sep = "") %>% 
  
  select(study, application, route, dose, n, name, time, value = apap, sigma = apap_se) %>% 
  filter(!is.na(value)) %>% 
  {.}

data_2 <- fitErrorModel(data_2, factors = c("study", "application", "route", "dose"), plotting = F)

plotData(as.datalist(data_2))


doses <- data.frame(unique(data_2[c("study", "application", "route", "dose")])[-4] %>% as.list, 
                dose = as.character(c(650, 650, 1500,5600,1400,1000,1000,2000,500)),
                dosepar = c(rep("PODOSE_apap", 5), "IVDOSE_apap", rep("PODOSE_apap", 3)),
                stringsAsFactors = F)


data_2

data_2 <-
  rbind(
  left_join(data_2 %>% select(-dose), doses) %>% filter(!str_detect(study, "Rawlins1977")), 
  right_join(data_2, doses) %>% filter(!is.na(value))
)
data_2 <-  data_2 %>% select(-n)

plotData(as.datalist(data_2))
```


## Prepare conditions
```{r, warning=FALSE}
covtable <- data_2 %>% as.datalist() %>% covariates()

dosepars <- doses$dosepar %>% unique

outer_pars <- sort(c(dosepars, pars_to_optimize))


trafo <-
  pars %>% 
  sort_by_name() %>% 
  replace((names(.) %in% outer_pars), outer_pars) %>% 
  branch(covtable) %>% 
  define("dosepar~DOSE_study_dose", dosepar = dosepar, dose = dose, study = study) %>% #insert values for the doses
  insert("remainingdosepar~0", remainingdosepar = dosepars) %>% # replace the other dose_par by zero
  
  insert("x~x_study_application", x = "Ka_apap", study = study, application = application) %>% 
  
  # insert("x~exp(X)", x = pars_to_optimize, X = toupper(pars_to_optimize)) 
  insert("x~exp(X)", x = mytrafo[[i]][is.na(as.numeric(mytrafo[[i]]))], X = toupper(mytrafo[[i]][is.na(as.numeric(mytrafo[[i]]))]))  # hacking insert()..., ignore the warnings, they're wanted :)

# trafo %>% head(1)
p_2 <- P(trafo)



mypars_2 <- getParameters(p_2) %>% are_names_of(0)



```



## Fit
Fit with condition specific Ka_apap and Dosing

Apply a l2 prior on the dose.
```{r}
obj <- normL2(data_2 %>% as.datalist, (g*x_2*p_2))

mypars_2[str_detect(names(mypars_2), "DOSE")] <-  names(mypars_2[str_detect(names(mypars_2), "DOSE")]) %>% str_extract("\\d{3,4}$") %>% as.numeric() %>% log()

constraint <- constraintL2(mypars_2[str_detect(names(mypars_2), "DOSE")], sigma = .5) # set L2 constraint on the dose_parameters

# myfits_2 <- runbg({mstrust((obj+constraint), mypars_2, "third_fits", result_path = "third_fits", sd = 3, fits = 96, cores = detectFreeCores(), blather = T)}, machine = "knecht6")
```


```{r, eval=TRUE}
myfits_2 %>% as.parframe() %>% head(7)

```




### Plot des erstbesten Fits
Zuerst die Parameter
```{r, eval=TRUE}
myfits_2 %>% as.parframe() %>% as.parvec() %>% exp
```

```{r, eval=TRUE}
plotCombined((g*x*p_2)(times, myfits_2 %>% as.parframe() %>% as.parvec(1), deriv = F), data = data_2 %>% as.datalist, name %in% c("apap"))+ 
  ggtitle(paste("           -2LL =", myfits_2 %>% as.parframe() %>% .[1,"value"] %>% unlist %>% round(2)))
## plotly::ggplotly()
```


### Plot des zweitbesten Fits
Unterschied in Baraka 1990

```{r, eval=TRUE}
myfits_2 %>% as.parframe(5) %>% as.parvec() %>% exp
```

```{r, eval=TRUE}
plotCombined((g*x*p_2)(times, myfits_2 %>% as.parframe() %>% as.parvec(5), deriv = F), data = data_2 %>% as.datalist, name %in% c("apap"))+ 
  ggtitle(paste("           -2LL =", myfits_1 %>% as.parframe() %>% .[5,"value"] %>% unlist %>% round(2)))
## plotly::ggplotly()
```



```{r}
# save.image(file = tpaste0("workspace.rda"))
```







